Mamary Gland Development Exploratory Data Analysis

### 2017-06-23 src/QCAnalysis.Rmd
added fdkeep

pD <- mutate(pD,
	     PassViability=prcntMito < ThresholdViability,
	     PassGenesDet=GenesDetected > ThresholdGenesDet,
	     PassLibSize=UmiSums > ThresholdLibSize,
	     PassAll= PassViability & PassGenesDet & PassLibSize & bc.obs.Freq == 1)
table(pD$PassViability,pD$SampleID)
table(pD$PassGenesDet,pD$SampleID)
table(pD$PassLibSize,pD$SampleID)
table(pD$PassAll,pD$SampleID)
```

>>>>

pD <- mutate(pD,
	     PassViability=prcntMito < ThresholdViability,
	     PassGenesDet=GenesDetected > ThresholdGenesDet,
	     PassLibSize=UmiSums > ThresholdLibSize,
	     PassAll= PassViability & PassGenesDet & PassLibSize & bc.obs.Freq == 1)
table(pD$PassViability,pD$SampleID)
table(pD$PassGenesDet,pD$SampleID)
table(pD$PassLibSize,pD$SampleID)
table(pD$PassAll,pD$SampleID)

### FD
fD$keep <- rowSums(m) > 0.01
```
